---
title: "Developing Data Products Project"
author: "Tim Brennan"
date: "5/4/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Car MPG Predictor

This presentation is being created as part of the peer assessment for the coursera developing data products class. The assignment is geared toward ensuring the following concepts were well understood by the students.

- shiny to build data product application.
- R-Presentation or slidify to create data product related presentations.

## The Application

To display the understanding of using shiny to build an application, a simple application called Cars MPG Predictor has been developed and deployed at: [https://brennantim.shinyapps.io/MPGPredictor/](https://brennantim.shinyapps.io/MPGPredictor/)

The application allows the user to:

- Select variables cylinders, horsepower, weight and transmission type.
- Receive a prediciton as to the likely MPG a car will get based on input parameters.

## The Data

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

The dataset is included in the R datasets package and was used serveral times during the Johns Hopkins Data Science Specializationg track on Coursera.

Source code for the project is available on [GitHub](https://github.com/brennantim/dataproducts/tree/master/MPGPredictor).

##  The Functionality

```{r, echo=TRUE, eval=FALSE}
mtcars$am <- as.factor(mtcars$am)
levels(mtcars$am) <- c("Automatic", "Manual")
fit  <- lm(mpg~am + wt + hp + cyl, data = mtcars)

MPG <- function(am, wt, hp, cyl) {
        df.new <- data.frame(am=am, wt=wt, hp=hp, cyl=cyl)
        return(predict(fit, df.new))
}
```